---
title: "Codebook "
date: "30 avril 2017"
output: html_document
---

```{r, echo=FALSE }
knitr::opts_chunk$set(error = TRUE)
```
## Original data

The original data files come from  "/data/UCI HAR Dataset" directory, which has been 
downloaded from <https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip>

We use in this homework the following files:

1. Info

- README.txt
  
1. Variables:

- activity_labels.txt
- features.txt
- features_info.txt


2. Mesures :

- test/X_test.txt
- test/y_test.txt
- train/X_train.txt
- train/y_train.txt
- train/subject_train.txt
- test/subject_test.txt
 
 
## The result of analysis is two tables:


###mean_std:
```{r}
mean_std<-read.table("./data/join_mean_std.txt")
str(mean_std)
```


### tidy_t
```{r}
tidy_t<-read.table("./data/data_group_means.txt")
str(tidy_t)
```

## Data process

mean_std and tidy_t tables were performed following the instructions asked:

1.Merges the training and the test sets to create three  data sets.
    
    X_train.txt and X_test.txt
    subject_train.txt and subject_test.txt
    y_train.txt and y_test.txt


2.Extracts the variables which mesure the mean and standard deviation for each measurement.
    
    select the rows of features table with mean() and std() labels.
    select the columns of the mesures table (X_train.txt and X_test.txt).
    named the columns of the mesure with mean and std labels.

3.Uses descriptive activity names to name the activities in the data set.
    
    Create a table with an activity label and the name of the activity(LAYING,...).

4.Appropriately labels the data set with descriptive variable names.
    
    Finaly join the colums of the tree tables(subject_train_test, train_test_label,       mean_std_train_test) an get mean_std.
    Save mean_std.

5.From the data set in step 4, creates a second, independent tidy data set with the       average of each variable for each activity and each subject.
    
    We group the mean_std table by subject and activity columns then calculate the        mean of each mesures and get tidy_t table. 
    Save tidy_t.




 

